The very dependent recursive structure of iterated parametricity in indexed form

### 2025-12-29 paper/paper.tex
paper: mention zero case when finalizing construction

Therefore, assuming a construction of $\framep[n][n]$ from $D:\Xto{m}{n}$, we are able to build a $\framep[n+1][n+1]$ from $D$ extended with some $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U$. This is enough to build $\Xcomp{m}{n}(D)$, for $D:\Xto{m}{n}$, and thus $\Xp{m}$, by starting with an empty $D$.

>>>>

Therefore, assuming a construction of $\framep[n][n]$ from $D:\Xto{m}{n}$, we are able to build a $\framep[n+1][n+1]$ from $D$ extended with some $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U$. This is enough to build $\Xcomp{m}{n}(D)$, for $D:\Xto{m}{n}$, and thus $\Xp{m}$, by starting with an empty $D$, since, obviously, all fields of the structure are trivially inhabited by $\kstar$ when $n$ is $0$.
